\section{Discussion}
\label{sec:discussion}

\para{Adversarial null results are boundaries---if the metric is valid.} Our results answer the research question directly: adversarial interventions that fail to induce misalignment do mark genuine, quantifiable robustness boundaries. The map is sharply model- and mode-specific, robustness is multi-dimensional, 11/20 pairs are invariants, and robustness tracks alignment method at the effect-size level. But the encoding reversal shows the entire enterprise hinges on measurement validity. The naive substring pipeline scored encoding as the single \emph{worst} mode (threshold $=1$ for all models, compliance $\to 1.0$); the LLM judge inverted it to one of the \emph{most} robust ($L_5$ compliance $\approx 0$ for 4/5 models). The ``null result''---models are not jailbroken by Base64---is a real robustness boundary that a weak metric mistook for a catastrophic vulnerability. This is precisely the misunderstanding confound the literature warns about~\citep{clearbias2025,conditional2026}, and it is the strongest vindication of our core claim: \emph{a robustness boundary is only trustworthy once the metric is validated.}

\para{What the map tells alignment scientists.} The validated map is a targeting signal. It ranks models on a common scale (\gpt $>$ \gemma $>$ \llama $>$ \qwen $>$ \mistral) and, more usefully, localizes each model's weakest mode: \gemma is strong on jailbreak but soft on persona, \gpt is impervious to jailbreak yet most penetrable on bias, and \mistral is fragile almost everywhere. Because encoding robustness is orthogonal to the instruction-pressure cluster, a defense that hardens a model against jailbreaks should not be assumed to transfer to out-of-distribution encodings, or vice versa. The \apo/deliberative-over-\aft ordering (0.77 vs.\ 0.58) is consistent with the refusal-brittleness story of~\citet{arditi2024refusal} and the deliberative-alignment robustness story of~\citet{vlaf2026}.

\para{Error analysis.} Three checks support the corrected map. First, substring false positives concentrate in encoding (0.69) and are low elsewhere (jailbreak 0.18, persona 0.07), so the correction is targeted rather than global. Second, \mistral's collapse is genuine, not a metric artifact: it produces fluent harmful content under persona and jailbreak, confirmed by the high judge agreement in those modes. Third, \gemma's encoding timeouts were API-side (a large model at high concurrency) and were re-collected; the completed data show \gemma genuinely resists encoded attacks ($L_5 = 0.000$).

\subsection{Limitations}

\para{No fine-tuning testbed.} Emergent misalignment's primary substrate---insecure-code SFT with LoRA-rank, seed-count, and steering-scale dials---needs GPU training and was out of scope under our CPU-only constraint. We mapped inference-time modes only. Weight-space thresholds (steering scale, refusal-direction ablation count, cold-start SFT-seed count) are the natural next axis and may not track inference-time ones.

\para{Statistical power.} Five models $\times$ four modes make the between-model Kruskal test ($p=0.29$) and the \apo-vs-\aft contrast ($p=0.10$) underpowered. The rankings and effect sizes are the reliable output, not significance. More models per alignment family would sharpen the alignment-method claim.

\para{Judge as ground truth.} The encoding correction relies on a single LLM judge (\gpt). We did not measure inter-judge or human agreement, though the substring--judge agreement was 0.82--0.93 on the modes where the substring metric is valid. Judge choice is known to materially affect results~\citep{clearbias2025}.

\para{Conditional and concealed nulls.} An inference-time invariant (\eg \gpt jailbreak $L_5 = 0.000$) could hide behind an untested trigger~\citep{conditional2026,sleeperagents2024}. We did not run the conditional-trigger re-probe, so ``invariant'' means invariant \emph{under this intensity ladder}, not provably unremovable. Prompt-based intensity is also coarse; an optimization-based ladder (\eg GCG) would give smoother change-points.

\para{Broader impact.} \ours is a defensive diagnostic: it tells red-teamers and alignment scientists where a model resists and where it does not. The failure modes we sweep are all documented in the public literature, and we report aggregate robustness statistics rather than releasing new attack strings. The main dual-use risk is that a robustness map also localizes weak spots; we mitigate this by emphasizing the methodological contribution---validated boundary measurement---over any specific attack. The clearest broader lesson is a cautionary one for the field: safety evaluations that are not noise- and validity-calibrated can invert their own conclusions, reporting robust behavior as a vulnerability or vice versa.
