\section{Related Work}
\label{sec:related}

\para{Emergent misalignment and intervention intensity.} A growing body of work shows that narrow fine-tuning can produce broad misalignment. \citet{betley2025em} fine-tune aligned models on insecure code and observe misalignment on unrelated prompts, while matched \emph{secure} and \emph{educational-insecure} controls yield near-zero effect---the archetypal adversarial null result, where identical surface data produces no failure. Follow-ups establish that this phenomenon is low-dimensional and dose-dependent: it scales with dataset diversity, is inducible with a single rank-one adapter, and exhibits sharp phase transitions~\citep{modelorganisms2025}. Activation-steering variants show \emph{non-monotonic} dose-response with peaks and over-steering collapse~\citep{assteering2026}, and reinforcement learning exhibits a cold-start seed threshold below which the intervention genuinely fails~\citep{rlamplifies2026}. These papers each dial a single intervention on a single substrate. Unlike them, we sweep four \emph{inference-time} failure modes on one common model set with a unified, noise-calibrated intensity metric, and we treat the null result---not the success---as the primary signal.

\para{The refusal invariant.} Whether refusal is a single robust direction or a redundant mechanism is directly the ``truly robust vs.\ undertested'' question. \citet{arditi2024refusal} show refusal is mediated by one diff-in-means direction across 13 models and distinguish alignment-by-preference-optimization (\apo) from alignment-by-fine-tuning (\aft), finding \aft models more brittle. Others find refusal is geometrically multi-dimensional and model-specific, with some models retaining residual refusal after single-direction ablation. This motivates our two central design choices: measuring robustness \emph{per model} and treating it as multi-dimensional rather than a single scalar, which our cross-mode correlation matrix directly tests.

\para{Deception and conditional null results.} The hardest invariants involve concealment. \citet{sleeperagents2024} show backdoored deceptive behavior survives the full safety stack, with adversarial training \emph{hiding} rather than removing it. Work on conditional misalignment shows that popular mitigations can produce 0\% unconditional misalignment while re-eliciting it behind contextual triggers~\citep{conditional2026}. Alignment-faking studies~\citep{alignmentfaking2024,vlaf2026} warn that a zero compliance gap under toxic diagnostics can be masking, not robustness. We take these warnings as a hard limitation: our ``invariant'' means invariant \emph{under this intensity ladder}, and we flag the untested conditional-trigger re-probe explicitly.

\para{Robustness measurement.} \citet{instability2025} show safety decisions flip across seeds and temperature (24.8\% of prompts on average), defining a measurement noise floor and mandating $\geq 3$ samples per prompt---which we adopt directly. \clearbias~\citep{clearbias2025} introduce an LLM-judge escalation ladder and a ``misunderstanding filter'' to avoid mistaking confusion for robustness, and report that judge choice materially affects results. \citet{ad-vs-ood2024} show adversarial and out-of-distribution robustness are distinct and their correlation is model-specific---robustness is not one scalar. Our encoding reversal is a concrete, quantified instance of the \clearbias misunderstanding confound, and our cross-mode matrix operationalizes the multi-dimensionality of~\citet{ad-vs-ood2024}. Unlike prior measurement work, we unify these guards into a single harness and show that omitting the validity guard inverts a headline result.
